\subsection*{2025}
\begin{enumerate}
	 \item \href{https://www.jku.at/fileadmin/gruppen/108/ICAE_Working_Papers/wp172.pdf}{Bäuerle, L., \& Groenewald, M. M. (2025). From monoculture to pluricultures: Recent trends in economics education. (ICAE Working Paper Series; Nr. 172).}
	 \item \href{https://www.jku.at/fileadmin/gruppen/108/ICAE_Working_Papers/wp171.pdf}{Pühringer, S., \& Bäuerle, L. (2025). The Economics of Socio-Ecological Transformations: A conceptual framework. (ICAE Working Paper Series; Nr. 171).}
	 \item \href{https://www.jku.at/fileadmin/gruppen/108/ICAE_Working_Papers/wp170.pdf}{Bäuerle, L., \& Maasen, S. (2025). Transforming Economics from the Side Lane? The New Economy Space and its Thinktanks. (ICAE Working Paper Series; Nr. 170).}
	 \item \href{https://www.jku.at/fileadmin/gruppen/108/ICAE_Working_Papers/wp169.pdf}{Kapeller, J., \& Scharnreitner, F. (2025). A pluralist perspective on input-output modeling: searching for commensurability. (ICAE Working Paper Series; Nr. 169).}
	 \item \href{https://www.jku.at/fileadmin/gruppen/108/ICAE_Working_Papers/wp164.pdf}{Altreiter, C., Hager, T., \& Pühringer, S. (2025). Political Economy of Knowledge Production in Capitalist Academia: Challenges and Opportunities for Socio-Ecological Transformation. (ICAE Working Paper Series; Nr. 164).}
	 \item \href{https://www.jku.at/fileadmin/gruppen/108/ICAE_Working_Papers/wp162.pdf}{Cserjan, L., Eder, J. T., Hornykewycz, A., \& Porak, L. et al. (2025). Mobilitätswende produzieren: Produktionsbedingungen der österreichischen Bahnindustrie und industrielle Potenziale durch den Ausbau des öffentlichen Verkehrs. (ICAE Working Paper Series; Nr. 162).}
	 \item Pühringer, S., Aistleitner, M., Cserjan, L., \& Hieselmayr, S. (2025). Idiosyncrasies of the oligarchic elite: On the political economy of wealth concentration in Austria. (ICAE Working Paper Series; Nr. 157).
\end{enumerate}
\subsection*{2024}
\begin{enumerate}
	 \item Kapeller, J., Hornykewycz, A., Cserjan, L., \& Weber, J. D. (2024). Dekarbonisierung des Gebäudesektors als Teil einer sozial-ökologischen Transformation: ein Gestaltungsvorschlag. (ICAE Working Paper Series; Nr. 156).
	 \item Gräbner-Radkowitsch, C., \& Kapeller, J. (2024). Systemism. (ICAE Working Paper Series; Nr. 155).
	 \item Gräbner-Radkowitsch, C., \& Kapeller, J. (2024). Path Dependence. (ICAE Working Paper Series; Nr. 154).
	 \item Gräbner-Radkowitsch, C., \& Kapeller, J. (2024). The micro-macro link in heterodox economics. (ICAE Working Paper Series; Nr. 153).
\end{enumerate}
\subsection*{2023}
\begin{enumerate}
	 \item Pühringer, S., \& Wolfmayer, G. (2023). Organizers and promotors of academic competition? The role of (academic) social networks and platforms in the competitization of science. (ICAE Working Paper Series; Nr. 152).
	 \item Kapeller, J., \& Hubmann, G. (2023). Dilemmata marktliberaler Globalisierung – Globale Freiheit durch globalen Wettbewerb? (ICAE Working Paper Series; Nr. 151).
	 \item Pühringer, S., \& Wolfmayr, G. (2023). Competitive Performativity of (Academic) Social Networks. The subjectivation of Competition on ResearchGate, Google Scholar und Twitter. (ICAE Working Paper Series; Nr. 150).
	 \item Pühringer, S. (2023). Wie viel Wettbewerb wollen wir (uns leisten)? Zur Verwettbewerblichung der Universitäten in Österreich und darüber hinaus. (ICAE Working Paper Series; Nr. 149).
	 \item Hager, T., \& Pühringer, S. (2023). Gendered Competitive Practices in Economics. A Multi-Layer Model of Women’s Underrepresentation. (ICAE Working Paper Series; Nr. 148).
	 \item Hager, T., Mellacher, P., \& Rath, M. (2023). Endogenous Heterogeneous Gender Norms and the Distribution of Paid and Unpaid Work in an Intra-Household Bargaining Model. (S. 1-32). (ICAE Working Paper Series; Nr. 147).
	 \item Altreiter, C., Gräbner-Radkowitsch, C., Pühringer, S., \& Rogojanu, A. et al. (2023). The three faces of competitization: From marketization to a multiplicity of competition. (ICAE Working Paper Series; Nr. 146).
	 \item Porak, L., \& Reinke, R. (2023). The charm of emission trading: Ideas of German public economists on economic policy in times of crises. (ICAE Working Paper Series; Nr. 145).
\end{enumerate}
\subsection*{2022}
\begin{enumerate}
	 \item Gräbner-Radkowitsch, C., \& Strunk, B. (2022). Degrowth and the Global South? How institutionalism can complement a timely discourse on ecologically sustainable development in an unequal world. (ICAE Working Paper Series; Nr. 144).
	 \item Gräbner-Radkowitsch, C., Hager, T., \& Hornykewycz, A. (2022). Competing for sustainability? An institutionalist analysis of the new development model of the European Union. (ICAE Working Paper Series; Nr. 143).
	 \item Gräbner-Radkowitsch, C., \& Strunk, B. (2022). Degrowth and the global South: the twin problem of global dependencies. (ICAE Working Paper Series; Nr. 142).
	 \item Reiner, C. (2022). It’s the End of Globalization as We Know It! Zeitgemäße Betrachtungen zur politischen Ökonomik der Globalisierungskrise. (ICAE Working Paper Series; Nr. 141).
	 \item Reiner, C., \& Bellak, C. (2022). Hat die ökonomische Macht von Unternehmen in Österreich zugenommen? (ICAE Working Paper Series; Nr. 140).
	 \item Aistleitner, M. (2022). Development and Interdisciplinarity: re-examining the “economics silo”. (ICAE Working Paper Series; Nr. 139).
	 \item Schütz, B. (2022). Investment booms, diverging competitiveness and wage growth within a monetary union: An AB-SFC model. (ICAE Working Paper Series; Nr. 138).
	 \item Altreiter, C., Azevedo, S., Porak, L., \& Pühringer, S. et al. (2022). Winning urban competition with a social agenda. The competition imaginary in Viennese urban development plans. (ICAE Working Paper Series; Nr. 137).
	 \item Aistleitner, M., Kapeller, J., \& Kronberger, D. (2022). The Authors of Economics Journals Revisited: Evidence from a Large-Scale Replication of Hodgson \& Rothman (1999). (ICAE Working Paper Series; Nr. 136).
	 \item Gräbner-Radkowitsch, C., Hornykewycz, A., \& Schütz, B. (2022). The emergence of debt and secular stagnation in an unequal society: a stock- flow consistent agent-based approach. (ICAE Working Paper Series; Nr. 135).
	 \item Gräbner-Radkowitsch, C., Hornykewycz, A., \& Schütz, B. (2022). The emergence of debt and secular stagnation in an unequal society: a stockflow consistent agent-based approach. (ICAE Working Paper Series; Nr. 135).
	 \item Gräbner-Radkowitsch, C. (2022). Elements of an evolutionary approach to comparative economic studies: complexity, systemism, and path dependent development. (ICAE Working Paper Series; Nr. 134).
\end{enumerate}
\subsection*{2021}
\begin{enumerate}
	 \item Kapeller, J., Leitch, S., \& Wildauer, R. (2021). Is a 10 trillion euro European climate investment initiative fiscally sustainable? (ICAE Working Paper Series; Nr. 133).
	 \item Pühringer, S. (2021). Zur Pluralität der ökonomischen Politikberatung in Deutschland. (ICAE Working Paper Series; Nr. 132).
	 \item Kapeller, J., \& Gräbner-Radkowitsch, C. (2021). Standortwettbewerb und Deindustrialisierung: Das Beispiel MAN als Lehrbuchfall. (ICAE Working Paper Series; Nr. 131).
	 \item Gräbner, C., \& Hager, T. (2021). (Mis)Measuring Competitiveness: The Quantification of a Malleable Concept in the European Semester. (ICAE Working Paper Series; Nr. 130).
	 \item Kapeller, J., Leitch, S., \& Wildauer, R. (2021). A European Wealth Tax for a Fair and Green Recovery. (ICAE Working Paper Series; Nr. 129).
	 \item Hager, T., Heck, I., \& Rath, J. (2021). Competition in Transitional Processes: Polanyi \& Schumpeter. (ICAE Working Paper Series; Nr. 128).
	 \item Tamesberger, D., \& Theurl, S. (2021). Design and Take Up of Austria’s Coronavirus Short Time Work Model. (ICAE Working Paper Series; Nr. 127).
	 \item Porak, L. (2021). Governing the Ungovernable -- Recontextualizations of ‘Competition’ in European Policy Discourse. (ICAE Working Paper Series; Nr. 126).
	 \item Gräbner-Radkowitsch, C., \& Pühringer, S. (2021). Competition universalism: Its historical origins and timely alternatives. (ICAE Working Paper Series; Nr. 125).
	 \item Eder, J. (2021). Decreasing Dependency through Self-Reliance: Strengthening Local Economies through Community Wealth Building. (ICAE Working Paper Series; Nr. 124).
	 \item Pühringer, S., Porak, L., \& Rath, J. (2021). Talking about competition? Discursive shifts in the economic imaginary of competition in public debates. (ICAE Working Paper Series; Nr. 123).
	 \item Gräbner-Radkowitsch, C., Heimberger, P., Kapeller, J., \& Landesmann, M. et al. (2021). The evolution of debtor-creditor relationships within a monetary union: Trade imbalances, excess reserves and economic policy. (ICAE Working Paper Series; Nr. 122).
\end{enumerate}
\subsection*{2020}
\begin{enumerate}
	 \item Pühringer, S., Rath, J., \& Griesebner, T. (2020). The political economy of academic publishing: On the commodification of a public good. (ICAE Working Paper Series; Nr. 121).
	 \item Altreiter, C., Gräbner-Radkowitsch, C., Pühringer, S., \& Rogojanu, A. et al. (2020). Theorizing competition: an interdisciplinary framework. (ICAE Working Paper Series; Nr. 120).
	 \item Gräbner-Radkowitsch, C., Heimberger, P., \& Kapeller, J. (2020). Do the “smart kids” catch up? Technological capabilities, globalisation and economic growth. (ICAE Working Paper Series; Nr. 119).
	 \item Porak, L. (2020). Der größte ‘Trumpf’ Europas: Eine Analyse des ‘economic imaginary’ der Europäischen Kommission. (ICAE Working Paper Series; Nr. 118).
	 \item Altreiter, C., Gräbner-Radkowitsch, C., Pühringer, S., \& Rogojanu, A. et al. (2020). Theorizing Competition: an interdisciplinary approach. (ICAE Working Paper Series; Nr. 117).
	 \item Hager, T. (2020). Special Interest Groups \& Growth. (ICAE Working Paper Series; Nr. 116).
	 \item Hirte, K. (2020). Das doppelte Relexionsproblem in der Ökonomik. (S. 1-19). (ICAE Working Paper Series; Nr. 115).
	 \item Hirte, K. (2020). Friedman’s Instrumentalismus und das Problem von Kopernikus. (S. 1-25). (ICAE Working Paper Series; Nr. 114).
	 \item Gräbner-Radkowitsch, C., \& Hafele, J. (2020). The emergence of core-periphery structures in the European Union: a complexity perspective. (ICAE Working Paper Series; Nr. 113).
	 \item Schulmeister, S. (2020). Fixing long-term price paths for fossil energy – the optimal incentive for limiting global warming. (ICAE Working Paper Series; Nr. 112).
	 \item Wildauer, R., Leitch, S., \& Kapeller, J. (2020). How to boost the European Green Deal’s scale and ambition. (ICAE Working Paper Series; Nr. 111).
	 \item Aistleitner, M., \& Pühringer, S. (2020). Exploring the trade (policy) narratives in economic elite discourse. (ICAE Working Paper Series; Nr. 110).
	 \item Beyer, K., Griesser, M., \& Pühringer, S. (2020). Zwischen Meritokratie und Wohlfahrtschauvinismus. (ICAE Working Paper Series; Nr. 109).
	 \item Gräbner-Radkowitsch, C., \& Hornykewycz, A. (2020). Capability accumulation and product innovation: an agent-based perspective. (ICAE Working Paper Series; Nr. 108).
	 \item Rath, J. (2020). Substituting Trust by Technology: A Comparative Study. (ICAE Working Paper Series; Nr. 107).
	 \item Gräbner-Radkowitsch, C., Heimberger, P., \& Kapeller, J. (2020). Pandemic pushes polarisation: The Corona crisis and macroeconomic divergence in the Eurozone. (ICAE Working Paper Series; Nr. 106).
	 \item Aistleitner, M., Gräbner-Radkowitsch, C., \& Hornykewycz, A. (2020). Theory and Empirics of Capability Accumulation: Implications for Macroeconomic Modelling. (ICAE Working Paper Series; Nr. 105).
	 \item Kapeller, J., \& Gräbner-Radkowitsch, C. (2020). Konzernmacht in globalen Güterketten. (ICAE Working Paper Series; Nr. 104).
\end{enumerate}
\subsection*{2019}
\begin{enumerate}
	 \item Wildauer, R., \& Kapeller, J. (2019). A Comment on Fitting Pareto Tails to Complex Survey Data. (ICAE Working Paper Series; Nr. 102).
	 \item Wildauer, R., \& Kapeller, J. (2019). Rank Correction: A New Approach to Differential Non-Response in Wealth Survey Data. (ICAE Working Paper Series; Nr. 101).
	 \item Tamesberger, D., \& Theurl, S. (2019). Vorschlag für eine Jobgarantie für Langzeitarbeitslose in Österreich. (ICAE Working Paper Series; Nr. 100).
	 \item Kapeller, J., Gräbner-Radkowitsch, C., \& Heimberger, P. (2019). Economic Polarisation in Europe: Causes and Policy Options. (ICAE Working Paper Series; Nr. 99).
	 \item Kapeller, J., Gräbner, C., \& Heimberger, P. (2019). Wirtschaftliche Polarisierung in Europa: Ursachen und Handlungsoptionen. (ICAE Working Paper Series; Nr. 98).
	 \item Aistleitner, M., \& Pühringer, S. (2019). Exploring the trade narrative in top economics journals. (ICAE Working Paper Series; Nr. 97).
	 \item Raghavendra, S., \& Piiroinen, P. T. (2019). Confict as a closure: A Kaleckian model of growth and distribution under fnancialization. (ICAE Working Paper Series; Nr. 96).
	 \item Gräbner-Radkowitsch, C., Tamesberger, D., Heimberger, P., \& Kapelari, T. et al. (2019). Trade Models in the European Union. (ICAE Working Paper Series; Nr. 95).
	 \item Beyer, K., \& Pühringer, S. (2019). Divided we stand? Professional consensus and political conflict in academic economics. (ICAE Working Paper Series; Nr. 94).
	 \item Hirte, K. (2019). Das dritte Gossensche Gesetz. Zur Überlieferungspraxis in der ökonomischen Dogmengeschichte. (ICAE Working Paper Series; Nr. 93).
	 \item Pühringer, S., \& Ötsch, W. (2019). Die Wirkmacht der „Liebe zum Markt”: Zum anhaltenden Einfluss ordoliberaler ÖkonomInnen-Netzwerke in Politik und Gesellschaft. (ICAE Working Paper Series; Nr. 92).
	 \item Flechtner, S., \& Gräbner-Radkowitsch, C. (2019). The heterogeneous relationship between income and inequality: a panel co-integration approach. (ICAE Working Paper Series; Nr. 91).
	 \item Gräbner, C. (2019). Unrealistic models and how to identify them: on accounts of model realisticness. (ICAE Working Paper Series; Nr. 90).
	 \item Gräbner, C., \& Ghorbani, A. (2019). Defining institutions -- A review and a synthesis. (ICAE Working Paper Series; Nr. 89).
	 \item Gräbner, C., Heimberger, P., \& Kapeller, J. (2019). Export performance, price comeptitiveness and technology: Revisiting the Kaldor paradox. (ICAE Working Paper Series; Nr. 88).
\end{enumerate}
\subsection*{2018}
\begin{enumerate}
	 \item Foissner, F. (2018). Folgen einer möglichen Abschaffung der Notstandshilfe in Oberösterreich. (ICAE Working Paper Series; Nr. 87).
	 \item Aistleitner, M., Grimm, C., \& Kapeller, J. (2018). Auftragsvergabe, Leistungsqualität und Kostenintensität im Schienenpersonenverkehr. (ICAE Working Paper Series; Nr. 86).
	 \item Buyinza, F., \& Kapeller, J. (2018). Household Electrification and Education Outcomes: Panel Evidence from Uganda. (ICAE Working Paper Series; Nr. 85).
	 \item Buyinza, F., Tibaingana, A., \& Mutenyo, J. (2018). Factors Affecting Acces to Formal Credit by Micro and Small Enterprises in Ugande. (ICAE Working Paper Series; Nr. 83).
	 \item Gräbner-Radkowitsch, C., \& Strunk, B. (2018). Pluralism in economics: its critiques and their lessons. (ICAE Working Paper Series; Nr. 82).
	 \item Schütz, B. (2018). Employment and the minimum wage: A pluralist approach. (ICAE Working Paper Series; Nr. 81).
	 \item Pühringer, S. (2018). The “eternal character” of austerity measures in European crisis policies. (ICAE Working Paper Series; Nr. 80).
	 \item Heimberger, P. (2018). The dynamic effects of fiscal consolidation episodes on income inequality: Evidence for 17 OECD Countries over 1978-2013. (ICAE Working Paper Series; Nr. 79).
	 \item Griesser, M. (2018). Arbeitsmarktpolitik als Gesellschaftspolitik. (ICAE Working Paper Series; Nr. 78).
	 \item Grimm, C., Kapeller, J., \& Pühringer, S. (2018). Paradigms and Policies: The state of economics in the german-speaking countries. (ICAE Working Paper Series; Nr. 77).
	 \item Gräbner-Radkowitsch, C., Heimberger, P., Kapeller, J., \& Schütz, B. (2018). Structural change in times of increasing openness: assessing path dependency in European economic integration. (ICAE Working Paper Series; Nr. 76).
	 \item Aigner, E., Aistleitner, M., Glötzl, F., \& Kapeller, J. (2018). The focus of academic economics: before and after the crisis. (ICAE Working Paper Series; Nr. 75).
\end{enumerate}
\subsection*{2017}
\begin{enumerate}
	 \item Gräbner-Radkowitsch, C., Elsner, W., \& Lascaux, A. (2017). To trust or to control: Informal value transfer systems and computational analysis in institutional economics. (ICAE Working Paper Series; Nr. 74).
	 \item Humer, S., Moser, M., \& Schnetzer, M. (2017). Inheritances and the Accumulation of Wealth in the Eurozone. (ICAE Working Paper Series; Nr. 73).
	 \item Ferschli, B., Kapeller, J., Schütz, B., \& Wildauer, R. (2017). Bestände und Konzentration privater Vermögen in Österreich. (ICAE Working Paper Series; Nr. 72).
	 \item Beyer, K., Grimm, C., Kapeller, J., \& Pühringer, S. (2017). Der deutsche Sonderweg im Fokus: Eine vergleichende Analyse der paradig¬matischen Struktur und der politischen Orientierung der deutschen und US-amerikanischen Ökonomie. (ICAE Working Paper Series; Nr. 71).
	 \item Grimm, C., Kapeller, J., \& Pühringer, S. (2017). Zum Profil der deutschsprachigen Volkswirtschaftslehre. (ICAE Working Paper Series; Nr. 70).
	 \item Gräbner-Radkowitsch, C. (2017). The Complexity of Economies and Pluralism in Economics. (ICAE Working Paper Series; Nr. 69).
	 \item Kapeller, J. (2017). Pluralism in Economics: Epistemological Rationales and Pedagogical Implementation. (ICAE Working Paper Series; Nr. 68).
	 \item Kapeller, J., \& Steinerberger, S. (2017). Stability, Fairness and Random Walks in the Bargaining Problem. (ICAE Working Paper Series; Nr. 67).
	 \item Kapeller, J., \& Steinerberger, S. (2017). Emergent Phenomena in Scientific Publishing: A Simulation Exercise. (ICAE Working Paper Series; Nr. 66).
	 \item Kapeller, J. (2017). Delayed by outsourcing? Zur Stabilität des Kapitalismus im 21. Jahrhundert. (ICAE Working Paper Series; Nr. 65).
	 \item Gräbner-Radkowitsch, C., Heimberger, P., Kapeller, J., \& Schütz, B. (2017). Is Europe disintegrating? Macroeconomic divergence, structural polarization, trade and fragility. (ICAE Working Paper Series; Nr. 64).
	 \item Gräbner-Radkowitsch, C. (2017). How to relate models to reality? An epistemological framework for the validation and verification of computational models. (ICAE Working Paper Series; Nr. 63).
	 \item Gräbner-Radkowitsch, C., Elsner, W., \& Lascaux, A. (2017). Trust and Social Control. Sources of cooperation, performance, and stability in informal value transfer systems. (ICAE Working Paper Series; Nr. 62).
	 \item Huber, J., Heimberger, P., \& Kapeller, J. (2017). From paradigms to policies: Economic models in the EU’s fiscal regulation framework. (ICAE Working Paper Series; Nr. 61).
	 \item Aistleitner, M., Kapeller, J., \& Steinerberger, S. (2017). Citation Patterns in Economics and Beyond: Assessing the Peculiarities of Economics from Two Scientometric Perspectives. (ICAE Working Paper Series; Nr. 60).
	 \item Gerhartinger, P., Haunschmid, P., \& Tamesberger, D. (2017). How to explain Wage Growth Slowdown in Austria? (ICAE Working Paper Series; Nr. 58).
	 \item Ötsch, W., \& Pühringer, S. (2017). Right-wing populism and market-fundamentalism. (ICAE Working Paper Series; Band 59).
\end{enumerate}
\subsection*{2016}
\begin{enumerate}
	 \item Kapeller, J., Schütz, B., \& Springholz, F. (2016). Internationale Tendenzen und Potentiale der Vermögensbesteuerung. (ICAE Working Paper Series; Nr. 57).
	 \item Beyer, K., \& Bräutigam, L. (2016). Das europäische Schattenbankensystem Typologisierung und die Bewertung regulatorischer Initiativen auf europäischer Ebene. (ICAE Working Paper Series; Nr. 56).
	 \item Heimberger, P., \& Kapeller, J. (2016). A model-based measurement device in European fiscal policy-making: The ontology and epistemology of potential output. (ICAE Working Paper Series; Nr. 55).
	 \item Grimm, C. (2016). Postdemokratie, Machtverhältnisse und Ökonomik. (ICAE Working Paper Series; Nr. 54).
	 \item Pühringer, S. (2016). Think Tank Networks of German Neoliberalism. (ICAE Working Paper Series; Nr. 53).
	 \item Pühringer, S. (2016). Still the queen of the social sciences? (ICAE Working Paper Series; Nr. 52).
	 \item Grimm, C. (2016). Wirtschaftspolitische Positionen österreichischer Parteien im historischen Verlauf. (ICAE Working Paper Series; Nr. 51).
	 \item Heimberger, P., \& Kapeller, J. (2016). The performativity of potential output. (ICAE Working Paper Series; Nr. 50).
	 \item Pühringer, S., \& Griesser, M. (2016). Has economics returned to being the “dismal science”? The changing role of economic thought in German labour market reforms. (ICAE Working Paper Series; Nr. 49).
	 \item Heimberger, P. (2016). Wirtschaftliche Stagnation als \glqq neue Normalsituation\grqq{}? (ICAE Working Paper Series; Nr. 48).
	 \item Heimberger, P., Kapeller, J., \& Schütz, B. (2016). What’s ‘structural’ about unemployment in Europe: On the Determinants of the European Commission’s NAIRU Estimates. (ICAE Working Paper Series; Nr. 47).
	 \item Aistleitner, M., Kapeller, J., \& Steinerberger, S. (2016). The Power of Scientometrics and the Development of Economics. (ICAE Working Paper Series; Nr. 46).
	 \item Kapeller, J. (2016). Internationaler Freihandel: Theoretische Ausgangspunkte und empirische Folgen. (ICAE Working Paper Series; Nr. 45).
	 \item Pühringer, S., \& Stelzer-Orthofer, C. (2016). Neoliberale Think Tanks als (neue) Akteure in österreichischen gesellschafts- und sozialpolitischen Diskursen. (ICAE Working Paper Series; Nr. 44).
	 \item Dobusch, L., Wandl, S., \& Kapeller, J. (2016). Monocular Accounting and its Discontents: The case of the stability and growth pact. (ICAE Working Paper Series; Nr. 43).
	 \item Heimberger, P. (2016). Die aktuelle Krise im wirtschaftshistorischen Vergleich mit der Großen Depression der 1930er-Jahre. (ICAE Working Paper Series; Nr. 42).
\end{enumerate}
\subsection*{2015}
\begin{enumerate}
	 \item Heimberger, P. (2015). Did Fiscal Consolidation Cause the Double-Dip Recession in the Euro Area? (ICAE Working Paper Series; Nr. 41).
	 \item Beyer, K., \& Bräutigam, L. (2015). Shadow Banking and the Offshore Nexus -- Some Considerations on the Systemic Linkages of Two Important Economic Phenomena. (ICAE Working Paper Series; Nr. 40).
	 \item Ötsch, W. (2015). Ökonomie und Moral. (ICAE Working Paper Series; Nr. 39).
	 \item Ötsch, W., \& Pühringer, S. (2015). Marktradikalismus als Politische Ökonomie. Wirtschaftswissenschaften und ihre Netzwerke in Deutschland ab 1945. (ICAE Working Paper Series; Nr. 38).
	 \item Kapeller, J., \& Gräbner-Radkowitsch, C. (2015). The Micro‐Macro Link in Heterodox Economics. (ICAE Working Paper Series; Nr. 37).
	 \item Kapeller, J., \& Schütz, B. (2015). Verteilungstendenzen im Kapitalismus: Nationale und Globale Perspektiven. (ICAE Working Paper Series; Nr. 36).
	 \item Pühringer, S. (2015). Wie wirken ÖkonomInnen und Ökonomik auf Politik und Gesellschaft? Darstellung des gesellschaftlichen und politischen Einflusspotenzials von ÖkonomInnen anhand eines „Performativen Fußabdrucks“. (ICAE Working Paper Series; Nr. 35).
	 \item Beyer, K. (2015). Emanzipation bei Marx und seine Kritik an Proudhon. (ICAE Working Paper Series; Nr. 34).
	 \item Aistleitner, M., Fölker, M., \& Kapeller, J. (2015). Die Macht der Wissenschaftsstatistik und die Entwicklung der Ökonomie. (ICAE Working Paper Series; Nr. 33).
	 \item Aistleitner, M., Fölker, M., Kapeller, J., \& Mohr, F. X. et al. (2015). Verteilung und Gerechtigkeit: Philosophische Perspektiven. (ICAE Working Paper Series; Nr. 32).
	 \item Pühringer, S. (2015). Markets as “ultimate judges” of economic policies -- Angela Merkel´s discourse profile during the economic crisis and the European crisis policies. (ICAE Working Paper Series; Nr. 31).
\end{enumerate}
\subsection*{2014}
\begin{enumerate}
	 \item Pühringer, S. (2014). Kontinuitäten neoliberaler Wirtschaftspolitik in der Krise. (ICAE Working Paper Series; Nr. 30).
	 \item Ötsch, W. (2014). Relationships are Constructed from Generalized Unconscious Social Images Kept in Steady Locations in Mental Space. (ICAE Working Paper Series; Nr. 29).
	 \item Kapeller, J., Schütz, B., \& Tamesberger, D. (2014). From Free to Civilized Markets: First Steps towards Eutopia. (ICAE Working Paper Series; Nr. 28).
	 \item Ötsch, W. (2014). Warum war Keynes so erfolgreich? Eine Darstellung anhand der Methode von Bruno Latour. (ICAE Working Paper Series; Nr. 27).
	 \item Kapeller, J. (2014). The return of the rentier. Review of: Piketty, Thomas (2014): Capital in the 21st century. Harvard University Press, 685 pages. (ICAE Working Paper Series; Nr. 26).
\end{enumerate}
\subsection*{2013}
\begin{enumerate}
	 \item Ötsch, W. (2013). Populismus und Demagogie. Mit Beispielen von Jörg Haider, Heinz–Christian Strache und Frank Stronach. (ICAE Working Paper Series; Nr. 25).
	 \item Nordmann, J. (2013). Die neoliberale Gesellschaft. Ein theoretischer Umriss. (ICAE Working Paper Series; Nr. 24).
	 \item Nordmann, J. (2013). Grenzen aktueller Krisendebatten Über Konstruktionen der öffentlichen Meinung und das Verhältnis von Sach‐ und Grundsatzdiskussionen in (neo)liberalen Demokratien. (ICAE Working Paper Series; Nr. 23).
	 \item Nordmann, J. (2013). Das neoliberale Selbst. Zur Genese und Kritik neuer Subjektkonstruktionen. (ICAE Working Paper Series; Nr. 22).
	 \item Beyer, K., \& Bräutigam, L. (2013). CDOs – A Critical Phenomenon of the Financial System in Crisis. (ICAE Working Paper Series; Nr. 21).
	 \item Pühringer, S. (2013). Aus den Vorhöfen der Macht in die Medien zur eigenen Partei. Formen der Einflussnahme von ÖkonomInnen auf Politik und Wirtschaft im Zuge der Finanz-­ und Wirtschaftskrisenpolitik. (ICAE Working Paper Series; Nr. 20).
	 \item Pühringer, S., \& Ötsch, W. (2013). Das Team Stronach. Eine österreichische Tea Party? (ICAE Working Paper Series; Nr. 19).
	 \item Pühringer, S., \& Hirte, K. (2013). ÖkonomInnen in der Finanzkrise -- Netzwerkanalytische Sicht auf die deutschsprachigen ÖkonomInnen in der Finanzkrise. (S. 1-21). (ICAE Working Paper Series; Nr. 18).
	 \item Beyer, K., \& Ötsch, W. (2013). Die Finanzkrise 2007-2009 als Krise von Schattenbanken. Eine einführende institutionelle Analyse. (ICAE Working Paper Series; Nr. 17).
	 \item Hirte, K. (2013). Mainstream, Orthodoxie und Heterodoxie -- Zur Klassifizierung der Wirtschaftswissenschaften. (ICAE Working Paper Series; Nr. 16).
	 \item Pühringer, S. (2013). The implementation of the European Fiscal Compact in Austria as a post-democratic phenomenon. (ICAE Working Paper Series; Nr. 15).
	 \item Pühringer, S., \& Hirte, K. (2013). The financial crisis as a tsunami. Discourse profiles of economists in the financial crisis. (ICAE Working Paper Series; Nr. 14).
	 \item Plaimer, W., \& Pühringer, S. (2013). Der Fiskalpakt und seine Implementation in Österreich. (ICAE Working Paper Series; Nr. 13).
	 \item Hirte, K. (2013). Zauberwort „Entkopplung“ – Ein Rückblick auf den Diskurs zur Agrarreform 2003 sowie die dortigen Diskrepanzen zwischen Versprechen und Wirkprinzipien der so genannten „Entkopplung“. (ICAE Working Paper Series; Nr. 12).
\end{enumerate}
\subsection*{2012}
\begin{enumerate}
	 \item Ötsch, W. (2012). The Deep Meaning of “Market”. A Key to Understand the Neoliberal-­‐Market-­‐ Radical Society. (ICAE Working Paper Series; Nr. 11).
	 \item Kapeller, J., \& Pühringer, S. (2012). Democracy in liberalism and neoliberalism. The case of Popper and Hayek. (ICAE Working Paper Series; Nr. 10).
	 \item Pühringer, S., \& Hirte, K. (2012). Erdbeben, Fieber und zarte Pflänzchen. Chronologischer Verlauf des Finanzkrisen‐Diskurses deutschsprachiger Ökonomen. (ICAE Working Paper Series; Nr. 9).
	 \item Ötsch, W. (2012). Die Macht der Ratingagenturen. (ICAE Working Paper Series; Nr. 8).
	 \item Ötsch, W. (2012). Marktradikalität. Der Diskurs von \glqq dem Markt\grqq{}. (ICAE Working Paper Series; Nr. 7).
\end{enumerate}
\subsection*{2011}
\begin{enumerate}
	 \item Pühringer, M., \& Pühringer, S. (2011). Solidarität im Kapitalismus. Zur Unmöglichkeit einer Forderung. (ICAE Working Paper Series; Nr. 6).
	 \item Ötsch, W. (2011). Politische Ökonomie und Gesellschaft. Eine theoriegeschichtliche Skizze. (ICAE Working Paper Series; Nr. 5).
	 \item Plaimer, W. (2011). Demokratiedefizit im Gesetzgebungsprozess budgetrelevanter Gesetze auf Bundesebene in Österreich. (ICAE Working Paper Series; Nr. 4).
	 \item Pühringer, S. (2011). Gleichheit versus Vielfalt. Ein konstruierter Widerspruch? (ICAE Working Paper Series; Nr. 3).
\end{enumerate}
\subsection*{2010}
\begin{enumerate}
	 \item Ötsch, W. (2010). Die Finanz-­ und Wirtschaftskrise seit 2007: Ein Überblick. (ICAE Working Paper Series; Nr. 2).
	 \item Ötsch, W., Hirte, K., \& Nordmann, J. (2010). Die Evolution des ökonomischen Wissens und des Wissens über den Kapitalismus. Performativity als Analyseinstrument: das Beispiel der Fabian Society, der Mont Pèlerin Society und der Chicagoer Schule. (ICAE Working Paper Series; Nr. 1).
\end{enumerate}
