\subsection*{2023}
\begin{enumerate}
	\item Altreiter, C., Gräbner-Radkowitsch, C., Pühringer, S., \& Rogojanu, A. et al. (2023). The three faces of competitization: From marketization to a multiplicity of competition. (SPACE Working Paper Series; Nr. 18).
	\item Pühringer, S., \& Wolfmayer, G. (2023). Competitive Performativity of Academic Social Networks. The Subjectification of Competition on Researchgate, Twitter and Google Scholar. (S. 1-25). (SPACE Working Paper Series; Nr. 19).
\end{enumerate}
\subsection*{2022}
\begin{enumerate}
	\item Aistleitner, M. (2022). Development and Interdisciplinarity: re-examining the “economic silo”. (SPACE Working Paper Series; Nr. 14).
	\item Altreiter, C., Azevedo, S., Porak, L., \& Pühringer, S. et al. (2022). Winning urban competition with a social agenda. The competition imaginary in Viennese urban development. (SPACE Working Paper Series; Nr. 13).
	\item Gräbner-Radkowitsch, C., Hager, T., \& Hornykewycz, A. (2022). Competing for sustainability? An institutionalist analysis of the new development model of the European Union. (SPACE Working Paper Series; Nr. 17).
	\item Hager, T., Heck, I., \& Rath, J. (2022). Polanyi and Schumpeter: Transitional Processes via Societal Spheres. (S. 1-25). (SPACE Working Paper Series; Nr. 16).
\end{enumerate}
\subsection*{2021}
\begin{enumerate}
	\item Aistleitner, M., \& Pühringer, S. (2021). Exploring the trade (policy) narratives in economic elite discourse. (S. 1-16). (SPACE Working Paper Series; Nr. 1).
	\item Altreiter, C., Gräbner, C., Pühringer, S., \& Rogojanu, A. et al. (2021). Theorizing Competition -- An interdisciplinary approach to the genesis of a contested concept. (SPACE Working Paper Series; Nr. 3).
	\item Altreiter, C., Gräbner, C., Pühringer, S., \& Rogojanu, A. et al. (2021). Theorizing Competition. An Interdisciplinary Framework. (SPACE Working Paper Series; Nr. 4).
	\item Gräbner, C., \& Hager, T. (2021). (Mis)Measuring Competitiveness: The Quantification of a Malleable Concept in the European Semester. (SPACE Working Paper Series; Nr. 10).
	\item Porak, L. (2021). Governing the Ungovernable. Recontextualizations of Competition in European Policy Discourse. (SPACE Working Paper Series; Nr. 8). https://www.jku.at/fileadmin/gruppen/108/ICAE\_Working\_Papers/wp126.pdf
\end{enumerate}
\subsection*{2020}
\begin{enumerate}
	\item Pühringer, S., Porak, L., \& Rath, J. (2020). Talking about Competition? Discursive Shifts in the Economic Imaginary of Competition in Public Debates. (SPACE Working Paper Series; Nr. 6).
\end{enumerate}
