\subsection*{2025}
\begin{enumerate}
    	 \item Pühringer S., Aistleitner M., Cserjan L., Hieselmayr S.: Idiosyncrasies of the oligarchic elite: On the political economy of wealth concentration in Austria, Serie Working Paper Series, Nr. 157, 2025
\end{enumerate}
\subsection*{2024}
\begin{enumerate}
    	 \item Kapeller J., Hornykewycz A., Cserjan L., Weber J.: Dekarbonisierung des Gebäudesektors als Teil einer sozial--ökologischen Transformation: ein Gestaltungsvorschlag, Serie ICAE Working Paper Series, Nr. 156, 2024
	 \item Gräbner--Radkowitsch C., Kapeller J.: The micro--macro link in heterodox economics, Serie Working Paper Series, Nr. 154, 2024
	 \item Gräbner--Radkowitsch C., Kapeller J.: Systemism, Serie Working Paper Series, Nr. 155, 2024
	 \item Gräbner--Radkowitsch C., Kapeller J.: Path Dependence, Serie Working Paper Series, Nr. 154, 2024
\end{enumerate}
\subsection*{2023}
\begin{enumerate}
    	 \item Pühringer S., Wolfmayr G.: Competitive Performativity of (Academic) Social Networks. The subjectivation of Competition on ResearchGate, Google Scholar und Twitter, Serie ICAE Working Paper Series, Nr. 150, 2023
	 \item Pühringer S., Wolfmayer G.: Organizers and promotors of academic competition? The role of (academic) social networks and platforms in the competitization of science, Serie ICAE Working Paper Series, Nr. 152, Seite(n) 1--21, 2023
	 \item Pühringer S., Wolfmayer G.: Competitive Performativity of Academic Social Networks. The Subjectification of Competition on Researchgate, Twitter and Google Scholar., Serie SPACE Working Paper Series, Nr. 19, Seite(n) 1--25, 2023
	 \item Pühringer S.: Wie viel Wettbewerb wollen wir (uns leisten)? Zur Verwettbewerblichung der Universitäten in Österreich und darüber hinaus, Serie ICAE Working Paper Series, Vol. 149, Seite(n) 1--19, 2023
	 \item Porak L., Reinke R.: The charm of emission trading: Ideas of German public economists on economic policy in times of crises, Serie ICAE Working Paper Series, Nr. 145, 2023
	 \item Kapeller J., Hubmann G.: Dilemmata marktliberaler Globalisierung – Globale Freiheit durch globalen Wettbewerb?, Serie ICAE Working Paper Series, Nr. 151, Seite(n) 1--18, 2023
	 \item Hager T., Pühringer S.: Gendered Competitive Practices in Economics. A Multi--Layer Model of Women’s Underrepresentation, Serie ICAE Working Paper Series, Vol. 148, Seite(n) 1--22, 2023
	 \item Hager T., Mellacher P., Rath M.: Endogenous Heterogeneous Gender Norms and the Distribution of Paid and Unpaid Work in an Intra--Household Bargaining Model, Serie ICAE Working Paper Series, Nr. 147, Seite(n) 1--32, 2023
	 \item Altreiter C., Gräbner--Radkowitsch C., Pühringer S., Rogojanu A., Wolfmayr G.: The three faces of competitization: From marketization to a multiplicity of competition, 2023
	 \item Altreiter C., Gräbner--Radkowitsch C., Pühringer S., Rogojanu A., Wolfmayr G.: The three faces of competitization: From marketization to a multiplicity of competition, Serie SPACE Working Paper Series, Nr. 18, 2023
\end{enumerate}
\subsection*{2022}
\begin{enumerate}
    	 \item Schütz B.: Investment booms, diverging competitiveness and wage growth within a monetary union: An AB--SFC model, Serie ICAE Working Paper Series, Nr. 138, 2022
	 \item Reiner C., Bellak C.: Hat die ökonomische Macht von Unternehmen in Österreich zugenommen?, 2022
	 \item Reiner C.: It’s the End of Globalization as We Know It! Zeitgemäße Betrachtungen zur politischen Ökonomik der Globalisierungskrise, 2022
	 \item Hager T., Heck I., Rath J.: Polanyi and Schumpeter: Transitional Processes via Societal Spheres, Serie SPACE Working Paper Series, Nr. 16, Seite(n) 1--25, 2022
	 \item Gräbner--Radkowitsch C., Strunk B.: Degrowth and the global South: the twin problem of global dependencies, Serie ICAE Working Paper Series, Nr. 142, 2022
	 \item Gräbner--Radkowitsch C., Strunk B.: Degrowth and the Global South? How institutionalism can complement a timely discourse on ecologically sustainable development in an unequal world, Serie ICAE Working Paper Series, Nr. 144, 2022
	 \item Gräbner--Radkowitsch C., Hornykewycz A., Schütz B.: The emergence of debt and secular stagnation in an unequal society: a stockflow consistent agent--based approach, 2022
	 \item Gräbner--Radkowitsch C., Hornykewycz A., Schütz B.: The emergence of debt and secular stagnation in an unequal society: a stock-- flow consistent agent--based approach, 2022
	 \item Gräbner--Radkowitsch C., Hager T., Hornykewycz A.: Competing for sustainability? An institutionalist analysis of the new development model of the European Union, Serie SPACE Working Paper Series, Nr. 17, 2022
	 \item Gräbner--Radkowitsch C., Hager T., Hornykewycz A.: Competing for sustainability? An institutionalist analysis of the new development model of the European Union, 2022
	 \item Gräbner--Radkowitsch C.: Elements of an evolutionary approach to comparative economic studies: complexity, systemism, and path dependent development, 2022
	 \item Altreiter C., Azevedo S., Porak L., Pühringer S., Wolfmayr G.: Winning urban competition with a social agenda. The competition imaginary in Viennese urban development plans, 2022
	 \item Altreiter C., Azevedo S., Porak L., Pühringer S., Wolfmayr G.: Winning urban competition with a social agenda. The competition imaginary in Viennese urban development, Serie SPACE Working Paper Series, Nr. 13, 2022
	 \item Aistleitner M., Kapeller J., Kronberger D.: The Authors of Economics Journals Revisited: Evidence from a Large--Scale Replication of Hodgson \& Rothman (1999), 2022
	 \item Aistleitner M.: Development and Interdisciplinarity: re--examining the “economics silo”, 2022
	 \item Aistleitner M.: Development and Interdisciplinarity: re--examining the “economic silo”, Serie SPACE Working Paper Series, Nr. 14, 2022
\end{enumerate}
\subsection*{2021}
\begin{enumerate}
    	 \item Tamesberger D., Theurl S.: Design and Take Up of Austria’s Coronavirus Short Time Work Model, 2021
	 \item Pühringer S., Porak L., Rath J.: Talking about competition? Discursive shifts in the economic imaginary of competition in public debates, 2021
	 \item Pühringer S.: Zur Pluralität der ökonomischen Politikberatung in Deutschland, 2021
	 \item Porak L.: Governing the Ungovernable. Recontextualizations of Competition in European Policy Discourse, in ICAE Linz, Serie SPACE Working Paper Series, Nr. 8, 2021
	 \item Porak L.: Governing the Ungovernable -- Recontextualizations of ‘Competition’ in European Policy Discourse, 2021
	 \item Kapeller J., Leitch S., Wildauer R.: Is a 10 trillion euro European climate investment initiative fiscally sustainable?, 2021
	 \item Kapeller J., Leitch S., Wildauer R.: A European Wealth Tax for a Fair and Green Recovery, 2021
	 \item Kapeller J., Gräbner--Radkowitsch C.: Standortwettbewerb und Deindustrialisierung: Das Beispiel MAN als Lehrbuchfall, 2021
	 \item Heimberger P., Gechert S.: Do Corporate Tax Cuts Boost Economic Growth?, Serie wiiw Working Papers, Nr. 201, forthcoming, doi/full/10.1080/09692290.2021.1904269, 2021
	 \item Heimberger P.: Do Higher Public Debt Levels Reduce Economic Growth?, Serie wiiw Working Papers, Nr. 211, 2021
	 \item Hager T., Heck I., Rath J.: Competition in Transitional Processes: Polanyi \& Schumpeter, Serie ICAE Working Paper Series, Nr. 128, 2021
	 \item Gräbner--Radkowitsch C., Pühringer S.: Competition universalism: Its historical origins and timely alternatives, 2021
	 \item Gräbner--Radkowitsch C., Heimberger P., Kapeller J., Landesmann M., Schütz B.: The evolution of debtor--creditor relationships within a monetary union: Trade imbalances, excess reserves and economic policy, in Universität Duisburg, Serie Ifso working paper, Nr. 10, 2021
	 \item Gräbner--Radkowitsch C., Heimberger P., Kapeller J., Landesmann M., Schütz B.: The evolution of debtor--creditor relationships within a monetary union: Trade imbalances, excess reserves and economic policy, 2021
	 \item Gräbner C., Hager T.: (Mis)Measuring Competitiveness: The Quantification of a Malleable Concept in the European Semester, Serie ICAE Working Paper Series, Nr. 130, 2021
	 \item Gräbner C., Hager T.: (Mis)Measuring Competitiveness: The Quantification of a Malleable Concept in the European Semester, Serie SPACE Working Paper Series, Nr. 10, 2021
	 \item Eder J.: Decreasing Dependency through Self--Reliance: Strengthening Local Economies through Community Wealth Building, 2021
	 \item Altreiter C., Gräbner C., Pühringer S., Rogojanu A., Wolfmayr G.: Theorizing Competition. An Interdisciplinary Framework, Serie SPACE Working Paper Series, Nr. 4, 2021
	 \item Altreiter C., Gräbner C., Pühringer S., Rogojanu A., Wolfmayr G.: Theorizing Competition -- An interdisciplinary approach to the genesis of a contested concept, Serie SPACE Working Paper Series, Nr. 3, 2021
	 \item Aistleitner M., Pühringer S.: Exploring the trade (policy) narratives in economic elite discourse, Serie SPACE Working Paper Series, Nr. 1, Seite(n) 1--16, 2021
\end{enumerate}
\subsection*{2020}
\begin{enumerate}
    	 \item Wildauer R., Leitch S., Kapeller J.: How to boost the European Green Deal’s scale and ambition, 2020
	 \item Schulmeister S.: Fixing long--term price paths for fossil energy – the optimal incentive for limiting global warming, 2020
	 \item Rath J.: Substituting Trust by Technology: A Comparative Study, Serie ICAE Working Paper Series, Nr. 107, 2020
	 \item Pühringer S., Rath J., Griesebner T.: The political economy of academic publishing: On the commodification of a public good, 2020
	 \item Pühringer S., Porak L., Rath J.: Talking about Competition? Discursive Shifts in the Economic Imaginary of Competition in Public Debates, Serie SPACE Working Paper Series, Nr. 6, 2020
	 \item Porak L.: Der größte ‘Trumpf’ Europas: Eine Analyse des ‘economic imaginary’ der Europäischen Kommission, 2020
	 \item Kapeller J., Gräbner--Radkowitsch C.: Konzernmacht in globalen Güterketten, 2020
	 \item Hornykewycz A., Gräbner--Radkowitsch C.: Capability Accumulation and Product Innovation: Agent--Based Perspective, Serie Rebuilding Macroeconomics Working Paper Series, Nr. 9, Seite(n) 1--22, 2020
	 \item Hirte K.: Friedman’s Instrumentalismus und das Problem von Kopernikus, Serie ICAE Working Paper Series, Nr. 114, Seite(n) 1--25, 2020
	 \item Hirte K.: Das doppelte Relexionsproblem in der Ökonomik, Serie ICAE Working Paper Series, Nr. 115, Seite(n) 1--19, 2020
	 \item Hager T.: Special Interest Groups \& Growth, Serie ICAE Working Paper Series, Nr. 116, 2020
	 \item Gräbner--Radkowitsch C., Hornykewycz A.: Capability accumulation and product innovation: an agent--based perspective, 2020
	 \item Gräbner--Radkowitsch C., Heimberger P., Kapeller J.: Pandemic pushes polarisation: The Corona crisis and macroeconomic divergence in the Eurozone, 2020
	 \item Gräbner--Radkowitsch C., Heimberger P., Kapeller J.: Do the “smart kids” catch up? Technological capabilities, globalisation and economic growth, 2020
	 \item Gräbner--Radkowitsch C., Hafele J.: The emergence of core--periphery structures in the European Union: a complexity perspective, 2020
	 \item Gräbner--Radkowitsch C., Hafele J.: Emergence of Core--Periphery Structures in the European Union: A Complexity Perspective, Serie Rebuilding Macroeconomics Working Paper Series, Nr. 17, Seite(n) 1--21, 2020
	 \item Beyer K., Griesser M., Pühringer S.: Zwischen Meritokratie und Wohlfahrtschauvinismus, Serie ICAE Working Paper Series, Nr. 109, 2020
	 \item Altreiter C., Gräbner--Radkowitsch C., Pühringer S., Rogojanu A., Wolfmayr G.: Theorizing competition: an interdisciplinary framework, 2020
	 \item Altreiter C., Gräbner--Radkowitsch C., Pühringer S., Rogojanu A., Wolfmayr G.: Theorizing Competition: an interdisciplinary approach, 2020
	 \item Aistleitner M., Pühringer S.: Exploring the trade (policy) narratives in economic elite discourse, 2020
	 \item Aistleitner M., Gräbner--Radkowitsch C., Hornykewycz A.: Theory and empirics of capability accumulation: implications for macroeconomics modelling, Serie Rebuilding Macroeconomics Working Paper Series, Nr. 6, Seite(n) 1--29, 2020
	 \item Aistleitner M., Gräbner--Radkowitsch C., Hornykewycz A.: Theory and Empirics of Capability Accumulation: Implications for Macroeconomic Modelling, 2020
\end{enumerate}
\subsection*{2019}
\begin{enumerate}
    	 \item Ötsch W., Pühringer S.: The anti--democratic logic of right--wing Populism and neoliberal market--fundamentalism, in Institut für Ökonomie, Cusanus Hochschule, Serie Working Paper Serie ök, Nr. 48, 2019
	 \item Wildauer R., Kapeller J.: Rank Correction: A New Approach to Differential Non--Response in Wealth Survey Data, 2019
	 \item Wildauer R., Kapeller J.: A Comment on Fitting Pareto Tails to Complex Survey Data, Serie ICAE Working Paper Series, Nr. 102, 2019
	 \item Tamesberger D., Theurl S.: Vorschlag für eine Jobgarantie für Langzeitarbeitslose in Österreich, Serie ICAE Working Paper Series, Nr. 100, 2019
	 \item Raghavendra S., Piiroinen P.: Confict as a closure: A Kaleckian model of growth and distribution under fnancialization, Serie ICAE Working Paper Series, Nr. 96, 2019
	 \item Pühringer S., Ötsch W.: Die Wirkmacht der „Liebe zum Markt”: Zum anhaltenden Einfluss ordoliberaler ÖkonomInnen--Netzwerke in Politik und Gesellschaft, 2019
	 \item Pühringer S., Ötsch W.: Die Wirkmacht der ''Liebe zum Markt'': Zum anhaltenden Einfluss ordoliberaler ÖkonomInnenNetzwerke in Politik und Gesellschaft., in Institut für Ökonomie, Cusanus Hochschule, Serie Working Paper Serie ök, Nr. 51, 2019
	 \item Kapeller J., Gräbner--Radkowitsch C., Heimberger P.: Economic Polarisation in Europe: Causes and Policy Options, 2019
	 \item Kapeller J., Gräbner C., Heimberger P.: Wirtschaftliche Polarisierung in Europa: Ursachen und Handlungsoptionen, Serie ICAE Working Paper Series, Nr. 98, 2019
	 \item Hirte K.: Das dritte Gossensche Gesetz. Zur Überlieferungspraxis in der ökonomischen Dogmengeschichte, Serie ICAE Working Paper Series, Nr. 93, Seite(n) 1--63, 2019
	 \item Heimberger P.: The Impact of Labour Market Institutions and Capital Accumulation on Unemployment: Evidence for the OECD, 1985--2013, Serie wiiw Working Papers, Nr. 164, 2019
	 \item Heimberger P.: Does economic globalisation affect income inequality? A meta--analysis, Serie wiiw Working Papers, Nr. 165, 2019
	 \item Gräbner--Radkowitsch C., Tamesberger D., Heimberger P., Kapelari T., Kapeller J.: Trade Models in the European Union, 2019
	 \item Gräbner C., Heimberger P., Kapeller J.: Export performance, price comeptitiveness and technology: Revisiting the Kaldor paradox, Serie ICAE Working Paper Series, Nr. 88, 2019
	 \item Gräbner C., Ghorbani A.: Defining institutions -- A review and a synthesis, Serie ICAE Working Paper Series, Nr. 89, 2019
	 \item Gräbner C.: Unrealistic models and how to identify them: on accounts of model realisticness, Serie ICAE Working Paper Series, Nr. 90, 2019
	 \item Flechtner S., Gräbner--Radkowitsch C.: The heterogeneous relationship between income and inequality: a panel co--integration approach, 2019
	 \item Beyer K., Pühringer S.: Divided we stand? Professional consensus and political conflict in academic economics, 2019
	 \item Beyer K., Pühringer S.: Divided we stand? Professional consensus and political conflict in academic economics, in Institut für Ökonomie, Cusanus Hochschule, Serie Working Paper Serie ök, Nr. 51, 2019
	 \item Aistleitner M., Pühringer S.: Exploring the trade narrative in top economics journals, Serie ICAE Working Paper Series, Nr. 97, 2019
\end{enumerate}
\subsection*{2018}
\begin{enumerate}
    	 \item Ötsch W., Pühringer S.: Marktfundamentalismus als Kollektivgedanke. Mises und die Ordoliberalen, in Institut für Ökonomie, Cusanus Hochschule, Bernkastel--Kues, Serie Working Paper Serie ök, Nr. 41, 2018
	 \item Ötsch W., Graupe S.: Der vergessene Lippmann: Politik, Propaganda und Markt, in Institut für Ökonomie, Cusanus Hochschule, Bernkastel--Kues, Serie Working Paper Serie ök, Nr. 39, 2018
	 \item Ötsch W.: Wissen und Nicht--Wissen angesichts ''des Marktes'': Das Konzept von Hayek, in Institut für Ökonomie, Cusanus Hochschule, Bernkastel--Kues, Serie Working Paper Serie ök, Vol. 43, 2018
	 \item Ötsch W.: Bilder in der Geschichte der Ökonomie: Das Beispiel der Metapher von der Wirtschaft als Maschine, in Institut für Ökonomie, Cusanus Hochschule, Bernkastel--Kues., Serie Working Paper Serie ök, Vol. 42, 2018
	 \item Schütz B.: Employment and the minimum wage: A pluralist approach, Serie ICAE Working Paper Series, Nr. 81, 2018
	 \item Pühringer S., Bäuerle L.: What economics education is missing: The real world, in Institut für Ökonomie, Cusanus Hochschule, Serie Working Paper Serie ök, Nr. 37, 2018
	 \item Pühringer S.: The “eternal character” of austerity measures in European crisis policies., 2018
	 \item Heimberger P.: The dynamic effects of fiscal consolidation episodes on income inequality: Evidence for 17 OECD Countries over 1978--2013, 2018
	 \item Gräbner--Radkowitsch C., Strunk B.: Pluralism in economics: its critiques and their lessons, 2018
	 \item Gräbner--Radkowitsch C., Heimberger P., Kapeller J., Springholz F.: Measuring Economic Openness: A review of existing measures and empirical practices, 2018
	 \item Gräbner--Radkowitsch C., Heimberger P., Kapeller J., Schütz B.: Structural change in times of increasing openness: assessing path dependency in European economic integration, 2018
	 \item Grimm C., Kapeller J., Pühringer S.: Paradigms and Policies: The state of economics in the german--speaking countries, 2018
	 \item Griesser M.: Arbeitsmarktpolitik als Gesellschaftspolitik, Serie ICAE Working Paper Series, Nr. 78, 2018
	 \item Foissner F.: Folgen einer möglichen Abschaffung der Notstandshilfe in Oberösterreich, Serie ICAE Working Paper Series, Nr. 87, 2018
	 \item Buyinza F., Tibaingana A., Mutenyo J.: Factors Affecting Acces to Formal Credit by Micro and Small Enterprises in Ugande, Serie ICAE Working Paper Series, Nr. 83, 2018
	 \item Buyinza F., Kapeller J.: Household Electrification and Education Outcomes: Panel Evidence from Uganda, Serie ICAE Working Paper Series, Nr. 85, 2018
	 \item Aistleitner M., Grimm C., Kapeller J.: Auftragsvergabe, Leistungsqualität und Kostenintensität im Schienenpersonenverkehr, Serie ICAE Working Paper Series, Nr. 86, 2018
	 \item Aigner E., Aistleitner M., Glötzl F., Kapeller J.: The focus of academic economics: before and after the crisis, Serie ICAE Working Paper Series, Nr. 75, 2018
	 \item Aigner E., Aistleitner M., Glötzl F., Kapeller J.: The Focus of Academic Economics: Before and After the Crisis, in Institute for New Economic Thinking (INET), Serie Institute for New Economic Thinking  Working Paper Series, 2018
\end{enumerate}
\subsection*{2017}
\begin{enumerate}
    	 \item Ötsch W., Pühringer S.: Right--wing populism and market--fundamentalism, Serie ICAE Working Paper Series, Vol. 59, 2017
	 \item Pühringer S., Ötsch W.: Neoliberalism and Right--wing Populism: conceptual analogies, in Institut für Ökonomie, Cusanus Hochschule, Bernkastel--Kues, Serie Working Paper Serie ök, Vol. 36, 2017
	 \item Pühringer S., Liedl B.: Argumentationsstrategien einer neoliberalen Reformagenda: Zum Diskursprofil der Agenda Austria in medialen Debatten, in Institut für Ökonomie, Cusanus Hochschule, Bernkastel--Kues, Serie Working Paper Serie ök, Vol. 27, 2017
	 \item Pühringer S., Griesser M.: From the ''planning euphoria'' to the ''bitter economic truth'': The transmission of economic ideas into German labour market policies in the 1960s and 2000s, in Institut für Ökonomie, Cusanus Hochschule, Bernkastel--Kues, Serie Working Paper Serie ök, Nr. 30, 2017
	 \item Pühringer S.: Think tank networks of German neoliberalism power structures in economics and economic policies in post--war Germany, in Institut für Ökonomie, Cusanus Hochschule, Bernkastel--Kues, Serie Working Paper Serie ök, Nr. 24, 2017
	 \item Pühringer S.: The “eternal character” of austerity measures in European crisis policies. Evidences from the Fiscal Compact discourse in Austria., in Institut für Ökonomie, Cusanus Hochschule, Bernkastel--Kues, Serie Working Paper Serie ök, Nr. 32, 2017
	 \item Kapeller J., Steinerberger S.: Stability, Fairness and Random Walks in the Bargaining Problem, 2017
	 \item Kapeller J., Steinerberger S.: Emergent Phenomena in Scientific Publishing: A Simulation Exercise, Serie ICAE Working Paper Series, Nr. 66, 2017
	 \item Kapeller J.: Pluralism in Economics: Epistemological Rationales and Pedagogical Implementation, Serie ICAE Working Paper Series, Nr. 68, 2017
	 \item Kapeller J.: Delayed by outsourcing? Zur Stabilität des Kapitalismus im 21. Jahrhundert, 2017
	 \item Humer S., Moser M., Schnetzer M.: Inheritances and the Accumulation of Wealth in the Eurozone, Serie ICAE Working Paper Series, Nr. 73, 2017
	 \item Huber J., Heimberger P., Kapeller J.: From paradigms to policies: Economic models in the EU’s fiscal regulation framework, Serie ICAE Working Paper Series, Nr. 61, 2017
	 \item Gräbner--Radkowitsch C., Heimberger P., Kapeller J., Schütz B.: Is Europe disintegrating? Macroeconomic divergence, structural polarization, trade and fragility, 2017
	 \item Gräbner--Radkowitsch C., Elsner W., Lascaux A.: Trust and Social Control. Sources of cooperation, performance, and stability in informal value transfer systems, 2017
	 \item Gräbner--Radkowitsch C., Elsner W., Lascaux A.: To trust or to control: Informal value transfer systems and computational analysis in institutional economics, 2017
	 \item Gräbner--Radkowitsch C.: The Complexity of Economies and Pluralism in Economics, 2017
	 \item Gräbner--Radkowitsch C.: How to relate models to reality? An epistemological framework for the validation and verification of computational models, 2017
	 \item Grimm C., Kapeller J., Pühringer S.: Zum Profil der deutschsprachigen Volkswirtschaftslehre, Serie ICAE Working Paper Series, Nr. 70, 2017
	 \item Gerhartinger P., Haunschmid P., Tamesberger D.: How to explain Wage Growth Slowdown in Austria?, 2017
	 \item Ferschli B., Kapeller J., Schütz B., Wildauer R.: Bestände und Konzentration privater Vermögen in Österreich, Serie ICAE Working Paper Series, Nr. 72, 2017
	 \item Beyer K., Grimm C., Kapeller J., Pühringer S.: Der deutsche Sonderweg im Fokus: Eine vergleichende Analyse der paradig¬matischen Struktur und der politischen Orientierung der deutschen und US--amerikanischen Ökonomie, Serie ICAE Working Paper Series, Nr. 71, 2017
	 \item Aistleitner M., Kapeller J., Steinerberger S.: Citation Patterns in Economics and Beyond: Assessing the Peculiarities of Economics from Two Scientometric Perspectives, 2017
\end{enumerate}
\subsection*{2016}
\begin{enumerate}
    	 \item Ötsch W.: Imaginierte Grundlagen bei Adam Smith, in Institut für Ökonomie, Cusanus Hochschule, Bernkastel--Kues, Serie Working Paper Serie ök, Nr. 19, 2016
	 \item Pühringer S., Stelzer--Orthofer C.: Neoliberale Think Tanks als (neue) Akteure in österreichischen gesellschafts-- und sozialpolitischen Diskursen, Serie ICAE Working Paper Series, Nr. 44, 2016
	 \item Pühringer S., Griesser M.: Has economics returned to being the “dismal science”? The changing role of economic thought in German labour market reforms, Serie ICAE Working Paper Series, Vol. 49, 2016
	 \item Pühringer S.: Think Tank Networks of German Neoliberalism, Serie ICAE Working Paper Series, Nr. 53, 2016
	 \item Pühringer S.: Still the queen of the social sciences?, Serie ICAE Working Paper Series, Nr. 52, 2016
	 \item Kapeller J., Schütz B., Springholz F.: Internationale Tendenzen und Potentiale der Vermögensbesteuerung, 2016
	 \item Kapeller J.: Internationaler Freihandel: Theoretische Ausgangspunkte und empirische Folgen, 2016
	 \item Heimberger P., Kapeller J., Schütz B.: What’s ‘structural’ about unemployment in Europe: On the Determinants of the European Commission’s NAIRU Estimates, 2016
	 \item Heimberger P., Kapeller J.: The performativity of potential output: pro--cyclicality and path dependency in coordinating European fiscal policies, in Institute for New Economic Thinking, Serie Institute for New Economic Thinking  Working Paper Series, Nr. 50, 2016
	 \item Heimberger P., Kapeller J.: The performativity of potential output, Serie ICAE Working Paper Series, Nr. 50, 2016
	 \item Heimberger P., Kapeller J.: A model--based measurement device in European fiscal policy--making: The ontology and epistemology of potential output, Serie ICAE Working Paper Series, Nr. 55, 2016
	 \item Heimberger P.: Wirtschaftliche Stagnation als ''neue Normalsituation''?, Serie ICAE Working Paper Series, Nr. 48, 2016
	 \item Heimberger P.: Die aktuelle Krise im wirtschaftshistorischen Vergleich mit der Großen Depression der 1930er--Jahre, Serie ICAE Working Paper Series, Nr. 42, 2016
	 \item Heimberger P.: Did Fiscal Consolidation Cause the Double Dip Recession in the Euro Area?, Serie wiiw Working Papers, Nr. 130, 2016
	 \item Grimm C.: Wirtschaftspolitische Positionen österreichischer Parteien im historischen Verlauf, Serie ICAE Working Paper Series, Nr. 51, 2016
	 \item Grimm C.: Postdemokratie, Machtverhältnisse und Ökonomik, Serie ICAE Working Paper Series, Nr. 54, 2016
	 \item Dobusch L., Wandl S., Kapeller J.: Monocular Accounting and its Discontents: The case of the stability and growth pact, Serie ICAE Working Paper Series, Nr. 43, 2016
	 \item Beyer K., Bräutigam L.: Das europäische Schattenbankensystem Typologisierung und die Bewertung regulatorischer Initiativen auf europäischer Ebene, 2016
	 \item Aistleitner M., Kapeller J., Steinerberger S.: The Power of Scientometrics and the Development of Economics, Serie ICAE Working Paper Series, Nr. 46, 2016
\end{enumerate}
\subsection*{2015}
\begin{enumerate}
    	 \item Ötsch W., Pühringer S.: Marktradikalismus als Politische Ökonomie. Wirtschaftswissenschaften und ihre Netzwerke in Deutschland ab 1945, Serie ICAE Working Paper Series, Nr. 38, 2015
	 \item Ötsch W.: Ökonomie und Moral, Serie ICAE Working Paper Series, Nr. 39, 2015
	 \item Pühringer S.: Wie wirken ÖkonomInnen und Ökonomik auf Politik und Gesellschaft? Darstellung des gesellschaftlichen und politischen Einflusspotenzials von ÖkonomInnen anhand eines „Performativen Fußabdrucks“, Serie ICAE Working Paper Series, Nr. 35, 2015
	 \item Pühringer S.: Markets as “ultimate judges” of economic policies -- Angela Merkel´s discourse profile during the economic crisis and the European crisis policies., Serie ICAE Working Paper Series, Nr. 31, 2015
	 \item Kapeller J., Schütz B.: Verteilungstendenzen im Kapitalismus: Nationale und Globale Perspektiven, 2015
	 \item Kapeller J., Gräbner--Radkowitsch C.: The Micro‐Macro Link in Heterodox Economics, 2015
	 \item Heimberger P.: Did Fiscal Consolidation Cause the Double--Dip Recession in the Euro Area?, Serie ICAE Working Paper Series, Nr. 41, 2015
	 \item Beyer K., Bräutigam L.: Shadow Banking and the Offshore Nexus -- Some Considerations on the Systemic Linkages of Two Important Economic Phenomena, Serie ICAE Working Paper Series, Nr. 40, 2015
	 \item Beyer K.: Emanzipation bei Marx und seine Kritik an Proudhon, Serie ICAE Working Paper Series, Nr. 34, 2015
	 \item Aistleitner M., Fölker M., Kapeller J., Mohr F., Pühringer S.: Verteilung und Gerechtigkeit: Philosophische Perspektiven, Serie ICAE Working Paper Series, Nr. 32, 2015
	 \item Aistleitner M., Fölker M., Kapeller J.: Die Macht der Wissenschaftsstatistik und die Entwicklung der Ökonomie, 2015
\end{enumerate}
\subsection*{2014}
\begin{enumerate}
    	 \item Ötsch W.: Warum war Keynes so erfolgreich? Eine Darstellung anhand der Methode von Bruno Latour, Serie ICAE Working Paper Series, Nr. 27, 2014
	 \item Ötsch W.: Relationships are Constructed from Generalized Unconscious Social Images Kept in Steady Locations in Mental Space, Serie ICAE Working Paper Series, Nr. 29, 2014
	 \item Pühringer S.: Kontinuitäten neoliberaler Wirtschaftspolitik in der Krise, Serie ICAE Working Paper Series, Nr. 30, 2014
	 \item Kapeller J., Schütz B., Tamesberger D.: From Free to Civilized Markets: First Steps towards Eutopia, Serie ICAE Working Paper Series, Nr. 28, 2014
	 \item Kapeller J.: The return of the rentier. Review of: Piketty, Thomas (2014): Capital in the 21st century. Harvard University Press, 685 pages, 2014
\end{enumerate}
\subsection*{2013}
\begin{enumerate}
    	 \item Ötsch W.: Populismus und Demagogie. Mit Beispielen von Jörg Haider, Heinz–Christian Strache und Frank Stronach, Serie ICAE Working Paper Series, Nr. 25, 2013
	 \item Thieme S., Hirte K.: Mainstream, Orthodoxie und Heterodoxie – Zur Klassifizierung der Wirtschaftswissenschaften, 2013
	 \item Pühringer S., Ötsch W.: Das Team Stronach. Eine österreichische Tea Party?, Serie ICAE Working Paper Series, Nr. 19, 2013
	 \item Pühringer S., Hirte K.: ÖkonomInnen in der Finanzkrise -- Netzwerkanalytische Sicht auf die deutschsprachigen ÖkonomInnen in der Finanzkrise, Serie ICAE Working Paper Series, Nr. 18, Seite(n) 1--21, 2013
	 \item Pühringer S., Hirte K.: The financial crisis as a tsunami. Discourse profiles of economists in the financial crisis., in ICAE Uni Linz, Serie ICAE Working Paper Series, Nr. 14, 2013
	 \item Pühringer S.: The implementation of the European Fiscal Compact in Austria as a post--democratic phenomenon., Serie ICAE Working Paper Series, Nr. 15, 2013
	 \item Pühringer S.: Aus den Vorhöfen der Macht in die Medien zur eigenen Partei. Formen der Einflussnahme von ÖkonomInnen auf Politik und Wirtschaft im Zuge der Finanz--­ und Wirtschaftskrisenpolitik., Serie ICAE Working Paper Series, Nr. 20, 2013
	 \item Plaimer W., Pühringer S.: Der Fiskalpakt und seine Implementation in Österreich, Serie ICAE Working Paper Series, Vol. 2, 2013
	 \item Nordmann J.: Grenzen aktueller Krisendebatten Über Konstruktionen der öffentlichen Meinung und das Verhältnis von Sach‐ und Grundsatzdiskussionen in (neo)liberalen Demokratien, 2013
	 \item Nordmann J.: Die neoliberale Gesellschaft. Ein theoretischer Umriss., Serie ICAE Working Paper Series, Nr. 24, 2013
	 \item Nordmann J.: Das neoliberale Selbst. Zur Genese und Kritik neuer Subjektkonstruktionen, Serie ICAE Working Paper Series, Nr. 22, 2013
	 \item Hirte K.: Zauberwort „Entkopplung“ – Ein Rückblick auf den Diskurs zur Agrarreform 2003 sowie die dortigen Diskrepanzen zwischen Versprechen und Wirkprinzipien der so genannten „Entkopplung“., Serie ICAE Working Paper Series, Nr. 12, 2013
	 \item Hirte K.: Mainstream, Orthodoxie und Heterodoxie -- Zur Klassifizierung der Wirtschaftswissenschaften., Serie ICAE Working Paper Series, Nr. 16, 2013
	 \item Beyer K., Ötsch W.: Die Finanzkrise 2007--2009 als Krise von Schattenbanken. Eine einführende institutionelle Analyse., Serie ICAE Working Paper Series, Nr. 17, 2013
	 \item Beyer K., Bräutigam L.: CDOs – A Critical Phenomenon of the Financial System in Crisis., Serie ICAE Working Paper Series, Nr. 21, 2013
\end{enumerate}
\subsection*{2012}
\begin{enumerate}
    	 \item Ötsch W.: The Deep Meaning of “Market”. A Key to Understand the Neoliberal--­‐Market--­‐ Radical Society., Serie ICAE Working Paper Series, Nr. 11, 2012
	 \item Ötsch W.: Marktradikalität. Der Diskurs von ''dem Markt'', Serie ICAE Working Paper Series, Nr. 7, 2012
	 \item Ötsch W.: Die Macht der Ratingagenturen, Serie ICAE Working Paper Series, Nr. 8, 2012
	 \item Pühringer S., Hirte K.: Erdbeben, Fieber und zarte Pflänzchen. Chronologischer Verlauf des Finanzkrisen‐Diskurses deutschsprachiger Ökonomen, in ICAE, JKU, Serie ICAE Working Paper Series, Nr. 9, Linz, 2012
	 \item Kapeller J., Schütz B.: Conspicuous consumption, inequality and debt: The nature of consumption--driven profit--led regimes, 2012
	 \item Kapeller J., Pühringer S.: Democracy in liberalism and neoliberalism. The case of Popper and Hayek., Serie ICAE Working Paper Series, Nr. 10, 2012
\end{enumerate}
\subsection*{2011}
\begin{enumerate}
    	 \item Ötsch W.: Politische Ökonomie und Gesellschaft. Eine theoriegeschichtliche Skizze, Serie ICAE Working Paper Series, Nr. 5, 2011
	 \item Pühringer S.: Gleichheit versus Vielfalt. Ein konstruierter Widerspruch?, Serie ICAE Working Paper Series, Nr. 3, 2011
	 \item Pühringer M., Pühringer S.: Solidarität im Kapitalismus. Zur Unmöglichkeit einer Forderung, Serie ICAE Working Paper Series, Nr. 6, 2011
	 \item Plaimer W.: Demokratiedefizit im Gesetzgebungsprozess budgetrelevanter Gesetze auf Bundesebene in Österreich, Serie ICAE Working Paper Series, Nr. 4, 2011
\end{enumerate}
\subsection*{2010}
\begin{enumerate}
    	 \item Ötsch W., Hirte K., Nordmann J.: Die Evolution des ökonomischen Wissens und des Wissens über den Kapitalismus. Performativity als Analyseinstrument: das Beispiel der Fabian Society, der Mont Pèlerin Society und der Chicagoer Schule, in ICAE, JKU, Serie ICAE Working Paper Series, Nr. 1, Linz, 2010
	 \item Ötsch W.: Die Finanz--­ und Wirtschaftskrise seit 2007: Ein Überblick, Serie ICAE Working Paper Series, Nr. 2, 2010
\end{enumerate}
